Events

### 2024-02-22 index.qmd
update

- [x] Why ARTEMIS electron data and Wind ion data?

@@

{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}

>>>>

- [x] Why ARTEMIS electron data and Wind ion data?
- [ ] Disagreement between anisotropy observed and predicted by the theory

## 02/22/2024

::: {.column-screen-inset layout-nrow="1"}
{{< embed notebooks/10_results.ipynb#fig-anisotropy >}}

{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp >}}
:::

::: {.column-screen-inset layout-nrow="1"}
{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-2d >}}

{{< embed notebooks/10_results.ipynb#fig-anisotropy-comp-i-e >}}
:::

@@

### 2024-02-22 notebooks/events/01.qmd
update

# 2019-04-07

@@

@@

Summary plot

::: {.column-screen-inset layout-nrow="1"}
![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)

![](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
:::

>>>>

# Encounter2 (2019-04-07)

@@

## Observations

@@

### Summary plot

::: {.column-screen-inset layout-nrow="1"}
![2019-04-05](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190405.png)

![2019-04-06](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190406.png)

![2019-04-07](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190407.png)

![2019-04-08](https://psp-gateway.jhuapl.edu/backend/data/summary_plots/Summary_Plot_20190408.png)
:::

## ARTEMIS

::: {.column-page layout-nrow="1"}
![](http://themis.ssl.berkeley.edu/themisdata/thg/l0/asi/2019/04/orbit_moon_2019-04-09_0024.gif)

![](http://themis.ssl.berkeley.edu/themisdata/thg/l0/asi/2019/04/orbit_moon_2019-04-12_0024.gif)
:::

## Scripts
